Variants of G\"{o}del's Ontological Proof \\ in a Natural Deduction Calculus

### 2016-09-12 Papers/InProgress/NaturalDeduction/GodProof-ND.tex
citations and references are working

The natural deduction style was chosen for four reasons. Firstly, presentations of G\"odel's proof are typically either informal or formalized in other styles of proof calculi (e.g. Fitting's tableaux \citep{fitting} or Sobel's sentential modal calculus \citep{sobel2}). Therefore, a formalization in natural deduction is a valuable complement to the existing presentations. Secondly, it makes the ontological proof accessible to people who are familiarized with a natural deduction style. Thirdly, as natural deduction is the style used by proof assistants such as Coq \citep{coq} and Isabelle \citep{isabelle}, natural deduction formalizations can be verified step-by-step in such proof assistants, and we have in fact done this \citep{CSRModalLogicCoq}. And finally, in comparison to other kinds of proof systems (e.g. resolution, tableaux, sequent calculi), natural deduction can be considered less technical, more human-readable and more intuitive, because it relies on natural principles of reasoning such as modus ponens (implication elimination) and reasoning by assumption (implication introduction); these qualities are conducive to rendering the formalizations of ontological arguments accessible to a wider audience.

@@

An early unpublished draft of Section \ref{newproof} of this paper,
prepared by Woltzenlogel Paleo in March 2013, served as the starting
point for two distinct but complementary research endeavours. Siders
and Woltzenlogel Paleo transformed that early draft into this paper,
aiming for human-readable and yet formal natural deduction proofs.
Benzm\"uller and Woltzenlogel Paleo, on the other hand, focused on the
verification of variants of G\"odel's ontological arguments using
higher-order automated reasoning tools, which quickly led to many
publications. The main automatically obtained results about G\"odel's
and Scott's proofs appeared in the European Conference on Artificial
Intelligence \citep{ECAI2014} and, two years later, a detailed
analysis of an inconsistency found in G\"odel's axioms was published
in the International Joint Conference on Artificial Intelligence
\citep{IJCAI2016}. The automatic verification of variants by Anderson,
Bjordal and H\'ajek, on the other hand were presented in the First
World Congress on Logic and Religion
\citep{WorldCongressLogicAndReligion} and published in
\citep{AndersonHajekControversy} and results related to the modal
collapse were reported in the 4th Word Congress on the Square of
Opposition \citep{SquareOfOpposition} and later published in
\citep{ModalCollapse}. More detailed reconstructions of Scott's
variant within the interactive proof assistants Isabelle and Coq were
relesed, respectively, in Isabellle's Archive of Formal Proofs
\citep{IsabelleGod} and in the Symposium of Computer Science in Russia
\citep{CSRModalLogicInCoq}. The popularity of the topic led to invited
talks and corresponding invited abstracts in the proceedings of
workshops \citep{WADT,WADTPreProceedings,IWIL} and summer schools
\citep{SpiritualQuest,ReasoningWebSummerSchool} as well as articles
targeting a more general audience \citep{AustrianComputerSociety}.
More recently, this line of research ventured into other types of
ontological arguments, and a computer-assisted reconstruction of an
argument by Leibniz will appear as a chapter in a book dedicated to
the 300th anniversary of Leibniz's death
\citep{LeibnizOntologicalProof}. The automatic verification of G\"odel's
and Scott's variants \citep{ECAI2014} was preceded by an automatic
verification of (a non-modal version of) Anselm's ontological argument
\citep{ZaltaOppenheimer}. However, whereas the complexity of G\"odel's
and Scott's arguments required the embedding of higher-order modal
logics into higher-order logics and the use of higher-order automated
reasoners, Anselm's argument greater simplicity enabled it to be
verified with a first-order prover. Anselm's argument has also been
formalized within the interactive proof assistant PVS \citep{Rushby}
and there has been a so far failed attempt to formalize Avicenna's
argument in PVS as well.

@@

@@

@@

@@

\bibitem[{\itshape Goedel(1970)}]{Goedel} 
G\"odel, K. Ontological Proof. In Kurt G\"odel Collected Works vol. III. Ed. Feferman et al., pp. 403--404, 139, 145 or {\itshape Appendix A. Notes in Kurt G\"odel's hand} in [Sobel 2001].

@@

@@

\bibitem[{\itshape Bentert \& Benzm\"uller \& Streit \& Woltzenlogel Paleo(2016)}]{LeibnizOntologicalProof}
Bentert, M. \& Benzm\"uller, C. \& Streit, D. \& Woltzenlogel Paleo, B. 2016. {\itshape Analysis of an Ontological Proof Proposed by Leibniz}. [to appear in]  Death and Anti-Death, Volume 14: Four Decades after Michael Polanyi, Three Centuries after G. W. Leibniz. ed. Tandy, C. Ria University Press. 
% @incollection{LeibnizOntologicalProof,
%   author      = {Bentert, Matthias and Benzm\"uller, Christoph and Streit, David and Woltzenlogel Paleo, Bruno},
%   title       = {Analysis of an Ontological Proof Proposed by Leibniz},
%   editor      = {Tandy, Charles},
%   booktitle   = {[to appear in] Death and Anti-Death, Volume 14: Four Decades after Michael Polanyi, Three Centuries after G. W. Leibniz},
%   publisher   = {Ria University Press},
%   address     = {},
%   isbn        = {978-1-934297-25-4},
%   pages       = {},
%   chapter     = {},
%   year = {2016},
%   note = {\textbf{[Invited]} }
% }

\bibitem[{\itshape Benzm\"uller \& Woltzenlogel Paleo(2016)}]{IJCAI2016}
Benzm\"uller, C. \& Woltzenlogel Paleo, B. 2016. {\itshape The Inconsistency in G\"odel's Ontological Argument: A Success Story for AI in Metaphysics}. International Joint Conference on Artificial Intelligence - IJCAI. 
% @inproceedings{IJCAI2016,
%   author = {Benzm?ller, C. and Woltzenlogel Paleo, B.},
%   title  = {The Inconsistency in G\"odel's Ontological Argument: A Success Story for AI in Metaphysics},
%   booktitle = {International Joint Conference on Artificial Intelligence - IJCAI},
%   keywords ={HOML,Bruno,COREA*},
%   year = {2016}
% }

\bibitem[{\itshape Benzm\"uller \& Weber \& Woltzenlogel Paleo(2016)}]{AndersonHajekControversy}
Benzm\"uller, C. \& Weber, L. \& Woltzenlogel Paleo, B. 2016. {\itshape Computer-Assisted Analysis of the Anderson-Hajek Ontological Controversy}. Logica Universalis. Springer. 
% @article{AndersonHajekControversy,
%     author = {Benzm?ller, Christoph and Weber, Leon and Woltzenlogel Paleo, Bruno},
%     title  = {Computer-Assisted Analysis of the Anderson-H?jek Ontological Controversy},
%     journal = {Logica Universalis},
%     publisher = {Springer},
%     issn = {1661-8297},
%     volume = {10},
%     year = {2016},
%     keywords = {Bruno,HOML},
%     pages = {1--10},
%     note = {\emph{Accepted for publication on the 28th of February 2016}}
% }

\bibitem[{\itshape Benzm\"uller \& Weber \& Woltzenlogel Paleo(2015)}]{WorldCongressLogicAndReligion}
Benzm\"uller, C. \& Weber, L. \& Woltzenlogel Paleo, B. 2015. {\itshape Computer-Assisted Analysis of the Anderson-Hajek Ontological Controversy}. 1st World Congress on Logic and Religion. 
% @inproceedings{WorldCongressLogicAndReligion,
%     author = {Benzm?ller, Christoph and Weber, Leon and Woltzenlogel Paleo, Bruno},
%     title  = {Computer-Assisted Analysis of the Anderson-H?jek Ontological Controversy},
%     booktitle = {1st World Congress on Logic and Religion},
%     year = {2015},
%     keywords = {Bruno,Abstract,HOML},
%     pages = {49--50}
% }

\bibitem[{\itshape Benzm\"uller \& Woltzenlogel Paleo(2014)}]{WADT}
Benzm\"uller, C. \& Woltzenlogel Paleo, B. 2014. {\itshape On Logic Embeddings and G\"odel's God}. Recent Trends in Algebraic Development Techniques. 
% @inproceeding{WADT,
%    author = {Benzm?ller, Christoph and Woltzenlogel Paleo, Bruno},
%    title  = {On Logic Embeddings and G?del's God},
%    booktitle = {Recent Trends in Algebraic Development Techniques},
%    year = {2014},
%    crossref = {ADT},
%    keywords = {Bruno,Invited,HOML},
%    note = {\textbf{[Invited]} }
% }

\bibitem[{\itshape Benzm\"uller \& Woltzenlogel Paleo(2015)}]{SpiritualQuest}
Benzm\"uller, C. \& Woltzenlogel Paleo, B. 2015. {\itshape Experiments in Computational Metaphysics: G\"odel's Proof of God's Existence}. Science and Spiritual Quest: Proceedings of the 9th All India Students' Conference on Science and Spiritual Quest (IIT Kharagpur, 30th October -- 1st November). vol. 9. pp. 23--40. 
% @inproceedings{SpiritualQuest,
%   author    = {Christoph Benzm?ller and Bruno Woltzenlogel Paleo},
%   title     = {Experiments in Computational Metaphysics: G?del's Proof of God's Existence},
%   booktitle = {Science and Spiritual Quest: Proceedings of the 9th All India Students' Conference on Science and Spiritual Quest (IIT Kharagpur, 30th October -- 1st November)},
%   year      = {2015},
%   crossref  = {SpiritualQuest},
%   volume    = {9},
%   keywords  = {Bruno,Invited,HOML},
%   note = {\textbf{[Invited]} },
%   pages = {23--40}
% }

\bibitem[{\itshape Benzm\"uller \& Woltzenlogel Paleo(2015)}]{ReasoningWebSummerSchool}
Benzm\"uller, C. \& Woltzenlogel Paleo, B. 2015. {\itshape Higher-Order Modal Logics: Automation and Applications}. Reasoning Web. Web Logic Rules - 11th International Summer School 2015, Berlin, Germany, July 31 - August 4, 2015, Tutorial Lectures. pp. 32--74. 
% @incollection{ReasoningWebSummerSchool,
%   author    = {Christoph Benzm{\"{u}}ller and
%                Bruno Woltzenlogel Paleo},
%   title     = {Higher-Order Modal Logics: Automation and Applications},
%   booktitle = {Reasoning Web. Web Logic Rules - 11th International Summer School
%                2015, Berlin, Germany, July 31 - August 4, 2015, Tutorial Lectures},
%   pages     = {32--74},
%   year      = {2015},
%   crossref  = {DBLP:conf/rweb/2015},
%   url       = {http://dx.doi.org/10.1007/978-3-319-21768-0_2},
%   doi       = {10.1007/978-3-319-21768-0_2},
%   timestamp = {Sat, 25 Jul 2015 15:58:28 +0200},
%   biburl    = {http://dblp.uni-trier.de/rec/bib/conf/rweb/BenzmullerP15},
%   bibsource = {dblp computer science bibliography, http://dblp.org},
%   keywords = {Bruno,HOML,Invited,DBLP}
% }

\bibitem[{\itshape Benzm\"uller \& Woltzenlogel Paleo(2015)}]{CSRModalLogicInCoq}
Benzm\"uller, C. \& Woltzenlogel Paleo, B. 2015. {\itshape Interacting with Modal Logics in the Coq Proof Assistant}. Computer Science - Theory and Applications - 10th International Computer Science Symposium in Russia, {CSR} 2015, Listvyanka, Russia, July   13-17, 2015, Proceedings. pp. 398--411. 
% @inproceedings{CSRModalLogicInCoq,
%   author    = {Christoph Benzm{\"{u}}ller and
%                Bruno Woltzenlogel Paleo},
%   title     = {Interacting with Modal Logics in the Coq Proof Assistant},
%   booktitle = {Computer Science - Theory and Applications - 10th International Computer
%                Science Symposium in Russia, {CSR} 2015, Listvyanka, Russia, July
%                13-17, 2015, Proceedings},
%   pages     = {398--411},
%   year      = {2015},
%   crossref  = {DBLP:conf/csr/2015},
%   url       = {http://dx.doi.org/10.1007/978-3-319-20297-6_25},
%   doi       = {10.1007/978-3-319-20297-6_25},
%   timestamp = {Tue, 23 Jun 2015 13:05:11 +0200},
%   biburl    = {http://dblp.uni-trier.de/rec/bib/conf/csr/BenzmullerP15},
%   bibsource = {dblp computer science bibliography, http://dblp.org},
%   keywords  = {Bruno,HOML,COREC,DBLP}
% }

\bibitem[{\itshape Benzm\"uller \& Woltzenlogel Paleo(2014)}]{ECAI2014}
Benzm\"uller, C. \& Woltzenlogel Paleo, B. 2014. {\itshape Automating G{\"{o}}del's Ontological Proof of God's Existence with Higher-order Automated Theorem Provers}. ECAI 2014 - 21st European Conference on Artificial Intelligence, 18-22 August 2014, Prague, Czech Republic - Including Prestigious Applications of Intelligent Systems (PAIS 2014), pp. 93--98. 
% @inproceedings{ECAI2014,
%   Author = {Christoph Benzm{\"{u}}ller and Bruno Woltzenlogel Paleo},
%   Bibsource = {dblp computer science bibliography, http://dblp.org},
%   Biburl = {http://dblp.uni-trier.de/rec/bib/conf/ecai/BenzmullerP14},
%   Booktitle = {{ECAI} 2014 - 21st European Conference on Artificial Intelligence, 18-22 August 2014, Prague, Czech Republic - Including Prestigious Applications of Intelligent Systems {(PAIS} 2014)},
%   Crossref = {DBLP:conf/ecai/2014},
%   Date-Modified = {2014-10-14 07:42:43 +0000},
%   Doi = {10.3233/978-1-61499-419-0-93},
%   Keywords = {Bruno,DBLP,COREA,HOML},
%   Pages = {93--98},
%   Timestamp = {Mon, 13 Oct 2014 13:39:42 +0200},
%   Title = {Automating G{\"{o}}del's Ontological Proof of God's Existence with Higher-order Automated Theorem Provers},
%   Url = {http://dx.doi.org/10.3233/978-1-61499-419-0-93},
%   Year = {2014},
%     note = {\textbf{[Nominated for Best Paper]} }
% }

\bibitem[{\itshape Benzm\"uller \& Woltzenlogel Paleo(2014)}]{SquareOfOpposition}
Benzm\"uller, C. \& Woltzenlogel Paleo, B. 2014. {\itshape Formalization and Automated Verification of G\"odel's Proof of God's Existence}. 4th World Congress on the Square of Opposition, pp. 24--25. 
% @inproceedings{SquareOfOpposition,
%    author = {Benzm?ller, Christoph and Woltzenlogel Paleo, Bruno},
%    title  = {Formalization and Automated Verification of G?del's Proof of God's Existence},
%    booktitle = {4th World Congress on the Square of Opposition},
%    year = {2014},
%    keywords = {Bruno,Abstract,HOML},
%    pages = {24--25}
% }

\bibitem[{\itshape Benzm\"uller \& Woltzenlogel Paleo(2014)}]{WADTPreProceedings}
Benzm\"uller, C. \& Woltzenlogel Paleo, B. 2014. {\itshape On Logic Embeddings and G\"odel's God}. 22nd International Workshop on Algebraic Development Techniques, pp. 8--9. 
% @inworkshopinvited{WADTPreProceedings,
%    author = {Benzm?ller, Christoph and Woltzenlogel Paleo, Bruno},
%    title  = {On Logic Embeddings and G?del's God},
%    booktitle = {22nd International Workshop on Algebraic Development Techniques},
%    year = {2014},
%    keywords = {Bruno,Abstract,Invited,HOML},
%    note = {\textbf{[Invited]} },
%    pages = {8--9},
%    url = {http://wadt2014.cs.ovgu.de/pre-proceedings.pdf}
% }

\bibitem[{\itshape Benzm\"uller \& Woltzenlogel Paleo(2016)}]{ModalCollapse}
Benzm\"uller, C. \& Woltzenlogel Paleo, B. 2016. {\itshape The Modal Collapse as a Collapse of the Modal Square of Opposition}. Studies in Universal Logic, Springer. pp. 1--7. 
% @article{ModalCollapse,
%    author = {Benzm?ller, Christoph and Woltzenlogel Paleo, Bruno},
%    title  = {The Modal Collapse as a Collapse of the Modal Square of Opposition},
%    journal = {Studies in Universal Logic},
%    publisher = {Springer},
%    issn = {2297-0282},
%    year = {2016},
%    keywords = {Bruno,HOML},
%    pages   =  {1--7},
%    note    = {\emph{Submitted in November 2014. Accepted for publication on the 28th of February 2016}}
% }

\bibitem[{\itshape Benzm\"uller \& Woltzenlogel Paleo(2013)}]{IsabelleGod}
Benzm\"uller, C. \& Woltzenlogel Paleo, B. 2013. {\itshape G{\"{o}}del's God in Isabelle/HOL}. Archive of Formal Proofs. 
% @article{IsabelleGod,
%   author    = {Benzm?ller, Christoph and Woltzenlogel Paleo, Bruno},
%   title     = {G{\"{o}}del's God in Isabelle/HOL},
%   journal   = {Archive of Formal Proofs},
%   year      = {2013},
%   volume    = {},
%   keywords  = {Bruno,DBLP,HOML},
%   url       = {http://afp.sourceforge.net/entries/GoedelGod.shtml},
%   timestamp = {Wed, 15 Oct 2014 15:14:28 +0200},
%   biburl    = {http://dblp.uni-trier.de/rec/bib/journals/afp/Benzmueller13},
%   bibsource = {dblp computer science bibliography, http://dblp.org}
% }

>>>>

The natural deduction style was chosen for four reasons. Firstly, presentations of G\"odel's proof are typically either informal or formalized in other styles of proof calculi (e.g. Fitting's tableaux \citep{fitting} or Sobel's sentential modal calculus \citep{sobel2}). Therefore, a formalization in natural deduction is a valuable complement to the existing presentations. Secondly, it makes the ontological proof accessible to people who are familiarized with a natural deduction style. Thirdly, as natural deduction is the style used by proof assistants such as Coq \citep{coq} and Isabelle \citep{isabelle}, natural deduction formalizations can be verified step-by-step in such proof assistants, and we have in fact done this \citep{CSRModalLogicInCoq}. And finally, in comparison to other kinds of proof systems (e.g. resolution, tableaux, sequent calculi), natural deduction can be considered less technical, more human-readable and more intuitive, because it relies on natural principles of reasoning such as modus ponens (implication elimination) and reasoning by assumption (implication introduction); these qualities are conducive to rendering the formalizations of ontological arguments accessible to a wider audience.

@@

An early unpublished draft of Section \ref{sec:newproof} of this paper,
prepared by Woltzenlogel Paleo in March 2013, served as the starting
point for two distinct but complementary research endeavours. Siders
and Woltzenlogel Paleo transformed that early draft into this paper,
aiming for human-readable and yet formal natural deduction proofs.
Benzm\"uller and Woltzenlogel Paleo, on the other hand, focused on the
verification of variants of G\"odel's ontological arguments using
higher-order automated reasoning tools, which quickly led to many
publications. The main automatically obtained results about G\"odel's
and Scott's proofs appeared in the European Conference on Artificial
Intelligence \citep{ECAI2014} and, two years later, a detailed
analysis of an inconsistency found in G\"odel's axioms was published
in the International Joint Conference on Artificial Intelligence
\citep{IJCAI2016}. The automatic verification of variants by Anderson,
Bjordal and H\'ajek, on the other hand were presented in the First
World Congress on Logic and Religion
\citep{WorldCongressLogicAndReligion} and published in
\citep{controversy} and results related to the modal
collapse were reported in the 4th Word Congress on the Square of
Opposition \citep{SquareOfOpposition} and later published in
\citep{ModalCollapse}. More detailed reconstructions of Scott's
variant within the interactive proof assistants Isabelle and Coq were
relesed, respectively, in Isabellle's Archive of Formal Proofs
\citep{IsabelleGod} and in the Symposium of Computer Science in Russia
\citep{CSRModalLogicInCoq}. The popularity of the topic led to invited
talks and corresponding invited abstracts in the proceedings of
workshops \citep{WADT,WADTPreProceedings,IWIL} and summer schools
\citep{SpiritualQuest,ReasoningWebSummerSchool} as well as articles
targeting a more general audience \citep{AustrianComputerSociety}.
More recently, this line of research ventured into other types of
ontological arguments, and a computer-assisted reconstruction of an
argument by Leibniz will appear as a chapter in a book dedicated to
the 300th anniversary of Leibniz's death
\citep{LeibnizOntologicalProof}. The automatic verification of G\"odel's
and Scott's variants \citep{ECAI2014} was preceded by an automatic
verification of (a non-modal version of) Anselm's ontological argument
\citep{ZaltaOppenheimer}. However, whereas the complexity of G\"odel's
and Scott's arguments required the embedding of higher-order modal
logics into higher-order logics and the use of higher-order automated
reasoners, Anselm's argument greater simplicity enabled it to be
verified with a first-order prover. Anselm's argument has also been
formalized within the interactive proof assistant PVS \citep{Rushby}
and there has been a so far failed attempt to formalize Avicenna's
argument in PVS as well.

@@

\bibitem[{\itshape Bentert \& Benzm\"uller \& Streit \& Woltzenlogel Paleo(2016)}]{LeibnizOntologicalProof}
Bentert, M. \& Benzm\"uller, C. \& Streit, D. \& Woltzenlogel Paleo, B. 2016. {\itshape Analysis of an Ontological Proof Proposed by Leibniz}. [to appear in]  Death and Anti-Death, Volume 14: Four Decades after Michael Polanyi, Three Centuries after G. W. Leibniz. ed. Tandy, C. Ria University Press.

@@

\bibitem[{\itshape Benzm\"uller \& Weber \& Woltzenlogel Paleo(2015)}]{WorldCongressLogicAndReligion}
Benzm\"uller, C. \& Weber, L. \& Woltzenlogel Paleo, B. 2015. {\itshape Computer-Assisted Analysis of the Anderson-Hajek Ontological Controversy}. 1st World Congress on Logic and Religion.

@@

%\bibitem[{\itshape Benzm\"uller \& Weber \& Woltzenlogel Paleo(2016)}]{AndersonHajekControversy}
%Benzm\"uller, C. \& Weber, L. \& Woltzenlogel Paleo, B. 2016. {\itshape Computer-Assisted Analysis of the Anderson-Hajek Ontological Controversy}. Logica Universalis. Springer.

\bibitem[{\itshape Benzm\"uller \& Woltzenlogel Paleo(2013a)}]{IWIL}
Benzm\"uller, C. \& Woltzenlogel Paleo, B. 2013a. {\itshape G{\"{o}}del's God on the Computer}. 10th International Workshop on the Implementation of Logics. pp. 1--2.

\bibitem[{\itshape Benzm\"uller \& Woltzenlogel Paleo(2013b)}]{IsabelleGod}
Benzm\"uller, C. \& Woltzenlogel Paleo, B. 2013b. {\itshape G{\"{o}}del's God in Isabelle/HOL}. Archive of Formal Proofs.

\bibitem[{\itshape Benzm\"uller \& Woltzenlogel Paleo(2014a)}]{WADT}
Benzm\"uller, C. \& Woltzenlogel Paleo, B. 2014a. {\itshape On Logic Embeddings and G\"odel's God}. Recent Trends in Algebraic Development Techniques.

\bibitem[{\itshape Benzm\"uller \& Woltzenlogel Paleo(2014b)}]{WADTPreProceedings}
Benzm\"uller, C. \& Woltzenlogel Paleo, B. 2014b. {\itshape On Logic Embeddings and G\"odel's God}. 22nd International Workshop on Algebraic Development Techniques, pp. 8--9.

\bibitem[{\itshape Benzm\"uller \& Woltzenlogel Paleo(2014c)}]{SquareOfOpposition}
Benzm\"uller, C. \& Woltzenlogel Paleo, B. 2014c. {\itshape Formalization and Automated Verification of G\"odel's Proof of God's Existence}. 4th World Congress on the Square of Opposition, pp. 24--25.

\bibitem[{\itshape Benzm\"uller \& Woltzenlogel Paleo(2014d)}]{ECAI2014}
Benzm\"uller, C. \& Woltzenlogel Paleo, B. 2014d. {\itshape Automating G{\"{o}}del's Ontological Proof of God's Existence with Higher-order Automated Theorem Provers}. ECAI 2014 - 21st European Conference on Artificial Intelligence, 18-22 August 2014, Prague, Czech Republic - Including Prestigious Applications of Intelligent Systems (PAIS 2014), pp. 93--98.

\bibitem[{\itshape Benzm\"uller \& Woltzenlogel Paleo(2015a)}]{CSRModalLogicInCoq}
Benzm\"uller, C. \& Woltzenlogel Paleo, B. 2015a. {\itshape Interacting with Modal Logics in the Coq Proof Assistant}. Computer Science - Theory and Applications - 10th International Computer Science Symposium in Russia, {CSR} 2015, Listvyanka, Russia, July   13-17, 2015, Proceedings. pp. 398--411.

\bibitem[{\itshape Benzm\"uller \& Woltzenlogel Paleo(2015b)}]{ReasoningWebSummerSchool}
Benzm\"uller, C. \& Woltzenlogel Paleo, B. 2015b. {\itshape Higher-Order Modal Logics: Automation and Applications}. Reasoning Web. Web Logic Rules - 11th International Summer School 2015, Berlin, Germany, July 31 - August 4, 2015, Tutorial Lectures. pp. 32--74.

\bibitem[{\itshape Benzm\"uller \& Woltzenlogel Paleo(2015c)}]{SpiritualQuest}
Benzm\"uller, C. \& Woltzenlogel Paleo, B. 2015c. {\itshape Experiments in Computational Metaphysics: G\"odel's Proof of God's Existence}. Science and Spiritual Quest: Proceedings of the 9th All India Students' Conference on Science and Spiritual Quest (IIT Kharagpur, 30th October -- 1st November). vol. 9. pp. 23--40.

\bibitem[{\itshape Benzm\"uller \& Woltzenlogel Paleo(2016a)}]{IJCAI2016}
Benzm\"uller, C. \& Woltzenlogel Paleo, B. 2016a. {\itshape The Inconsistency in G\"odel's Ontological Argument: A Success Story for AI in Metaphysics}. International Joint Conference on Artificial Intelligence - IJCAI.

\bibitem[{\itshape Benzm\"uller \& Woltzenlogel Paleo(2016b)}]{ModalCollapse}
Benzm\"uller, C. \& Woltzenlogel Paleo, B. 2016b. {\itshape The Modal Collapse as a Collapse of the Modal Square of Opposition}. Studies in Universal Logic, Springer. pp. 1--7.

@@

\bibitem[{\itshape G\"odel(1970)}]{Goedel} 
G\"odel, K. Ontological Proof. In Kurt G\"odel Collected Works vol. III. Ed. Feferman et al., pp. 403--404, 139, 145 or {\itshape Appendix A. Notes in Kurt G\"odel's hand} in [Sobel 2001].

@@

\bibitem[{\itshape Woltzenlogel Paleo(2013)}]{AustrianComputerSociety}
 Woltzenlogel Paleo, B. 2013. {\itshape Automated Verification and Reconstruction of G\"odel's Proof of God's Existence}. Journal of the Austrian Computer Society. pp. 4--6.

@@

% @incollection{LeibnizOntologicalProof,
%   author      = {Bentert, Matthias and Benzm\"uller, Christoph and Streit, David and Woltzenlogel Paleo, Bruno},
%   title       = {Analysis of an Ontological Proof Proposed by Leibniz},
%   editor      = {Tandy, Charles},
%   booktitle   = {[to appear in] Death and Anti-Death, Volume 14: Four Decades after Michael Polanyi, Three Centuries after G. W. Leibniz},
%   publisher   = {Ria University Press},
%   address     = {},
%   isbn        = {978-1-934297-25-4},
%   pages       = {},
%   chapter     = {},
%   year = {2016},
%   note = {\textbf{[Invited]} }
% }

% @inproceedings{IJCAI2016,
%   author = {Benzm?ller, C. and Woltzenlogel Paleo, B.},
%   title  = {The Inconsistency in G\"odel's Ontological Argument: A Success Story for AI in Metaphysics},
%   booktitle = {International Joint Conference on Artificial Intelligence - IJCAI},
%   keywords ={HOML,Bruno,COREA*},
%   year = {2016}
% }

% @article{AndersonHajekControversy,
%     author = {Benzm?ller, Christoph and Weber, Leon and Woltzenlogel Paleo, Bruno},
%     title  = {Computer-Assisted Analysis of the Anderson-H?jek Ontological Controversy},
%     journal = {Logica Universalis},
%     publisher = {Springer},
%     issn = {1661-8297},
%     volume = {10},
%     year = {2016},
%     keywords = {Bruno,HOML},
%     pages = {1--10},
%     note = {\emph{Accepted for publication on the 28th of February 2016}}
% }

% @inproceedings{WorldCongressLogicAndReligion,
%     author = {Benzm?ller, Christoph and Weber, Leon and Woltzenlogel Paleo, Bruno},
%     title  = {Computer-Assisted Analysis of the Anderson-H?jek Ontological Controversy},
%     booktitle = {1st World Congress on Logic and Religion},
%     year = {2015},
%     keywords = {Bruno,Abstract,HOML},
%     pages = {49--50}
% }

% @inproceeding{WADT,
%    author = {Benzm?ller, Christoph and Woltzenlogel Paleo, Bruno},
%    title  = {On Logic Embeddings and G?del's God},
%    booktitle = {Recent Trends in Algebraic Development Techniques},
%    year = {2014},
%    crossref = {ADT},
%    keywords = {Bruno,Invited,HOML},
%    note = {\textbf{[Invited]} }
% }

% @inproceedings{SpiritualQuest,
%   author    = {Christoph Benzm?ller and Bruno Woltzenlogel Paleo},
%   title     = {Experiments in Computational Metaphysics: G?del's Proof of God's Existence},
%   booktitle = {Science and Spiritual Quest: Proceedings of the 9th All India Students' Conference on Science and Spiritual Quest (IIT Kharagpur, 30th October -- 1st November)},
%   year      = {2015},
%   crossref  = {SpiritualQuest},
%   volume    = {9},
%   keywords  = {Bruno,Invited,HOML},
%   note = {\textbf{[Invited]} },
%   pages = {23--40}
% }

% @incollection{ReasoningWebSummerSchool,
%   author    = {Christoph Benzm{\"{u}}ller and
%                Bruno Woltzenlogel Paleo},
%   title     = {Higher-Order Modal Logics: Automation and Applications},
%   booktitle = {Reasoning Web. Web Logic Rules - 11th International Summer School
%                2015, Berlin, Germany, July 31 - August 4, 2015, Tutorial Lectures},
%   pages     = {32--74},
%   year      = {2015},
%   crossref  = {DBLP:conf/rweb/2015},
%   url       = {http://dx.doi.org/10.1007/978-3-319-21768-0_2},
%   doi       = {10.1007/978-3-319-21768-0_2},
%   timestamp = {Sat, 25 Jul 2015 15:58:28 +0200},
%   biburl    = {http://dblp.uni-trier.de/rec/bib/conf/rweb/BenzmullerP15},
%   bibsource = {dblp computer science bibliography, http://dblp.org},
%   keywords = {Bruno,HOML,Invited,DBLP}
% }

% @inproceedings{CSRModalLogicInCoq,
%   author    = {Christoph Benzm{\"{u}}ller and
%                Bruno Woltzenlogel Paleo},
%   title     = {Interacting with Modal Logics in the Coq Proof Assistant},
%   booktitle = {Computer Science - Theory and Applications - 10th International Computer
%                Science Symposium in Russia, {CSR} 2015, Listvyanka, Russia, July
%                13-17, 2015, Proceedings},
%   pages     = {398--411},
%   year      = {2015},
%   crossref  = {DBLP:conf/csr/2015},
%   url       = {http://dx.doi.org/10.1007/978-3-319-20297-6_25},
%   doi       = {10.1007/978-3-319-20297-6_25},
%   timestamp = {Tue, 23 Jun 2015 13:05:11 +0200},
%   biburl    = {http://dblp.uni-trier.de/rec/bib/conf/csr/BenzmullerP15},
%   bibsource = {dblp computer science bibliography, http://dblp.org},
%   keywords  = {Bruno,HOML,COREC,DBLP}
% }

% @inproceedings{ECAI2014,
%   Author = {Christoph Benzm{\"{u}}ller and Bruno Woltzenlogel Paleo},
%   Bibsource = {dblp computer science bibliography, http://dblp.org},
%   Biburl = {http://dblp.uni-trier.de/rec/bib/conf/ecai/BenzmullerP14},
%   Booktitle = {{ECAI} 2014 - 21st European Conference on Artificial Intelligence, 18-22 August 2014, Prague, Czech Republic - Including Prestigious Applications of Intelligent Systems {(PAIS} 2014)},
%   Crossref = {DBLP:conf/ecai/2014},
%   Date-Modified = {2014-10-14 07:42:43 +0000},
%   Doi = {10.3233/978-1-61499-419-0-93},
%   Keywords = {Bruno,DBLP,COREA,HOML},
%   Pages = {93--98},
%   Timestamp = {Mon, 13 Oct 2014 13:39:42 +0200},
%   Title = {Automating G{\"{o}}del's Ontological Proof of God's Existence with Higher-order Automated Theorem Provers},
%   Url = {http://dx.doi.org/10.3233/978-1-61499-419-0-93},
%   Year = {2014},
%     note = {\textbf{[Nominated for Best Paper]} }
% }

% @inproceedings{SquareOfOpposition,
%    author = {Benzm?ller, Christoph and Woltzenlogel Paleo, Bruno},
%    title  = {Formalization and Automated Verification of G?del's Proof of God's Existence},
%    booktitle = {4th World Congress on the Square of Opposition},
%    year = {2014},
%    keywords = {Bruno,Abstract,HOML},
%    pages = {24--25}
% }

% @inworkshopinvited{WADTPreProceedings,
%    author = {Benzm?ller, Christoph and Woltzenlogel Paleo, Bruno},
%    title  = {On Logic Embeddings and G?del's God},
%    booktitle = {22nd International Workshop on Algebraic Development Techniques},
%    year = {2014},
%    keywords = {Bruno,Abstract,Invited,HOML},
%    note = {\textbf{[Invited]} },
%    pages = {8--9},
%    url = {http://wadt2014.cs.ovgu.de/pre-proceedings.pdf}
% }

% @article{ModalCollapse,
%    author = {Benzm?ller, Christoph and Woltzenlogel Paleo, Bruno},
%    title  = {The Modal Collapse as a Collapse of the Modal Square of Opposition},
%    journal = {Studies in Universal Logic},
%    publisher = {Springer},
%    issn = {2297-0282},
%    year = {2016},
%    keywords = {Bruno,HOML},
%    pages   =  {1--7},
%    note    = {\emph{Submitted in November 2014. Accepted for publication on the 28th of February 2016}}
% }

% @article{IsabelleGod,
%   author    = {Benzm?ller, Christoph and Woltzenlogel Paleo, Bruno},
%   title     = {G{\"{o}}del's God in Isabelle/HOL},
%   journal   = {Archive of Formal Proofs},
%   year      = {2013},
%   volume    = {},
%   keywords  = {Bruno,DBLP,HOML},
%   url       = {http://afp.sourceforge.net/entries/GoedelGod.shtml},
%   timestamp = {Wed, 15 Oct 2014 15:14:28 +0200},
%   biburl    = {http://dblp.uni-trier.de/rec/bib/journals/afp/Benzmueller13},
%   bibsource = {dblp computer science bibliography, http://dblp.org}
% }

% @inworkshopinvited{IWIL,
%    author = {Benzm?ller, Christoph and Woltzenlogel Paleo, Bruno},
%    title  = {G?del's God on the Computer},
%    booktitle = {10th International Workshop on the Implementation of Logics},
%    year = {2013},
%    keywords = {Bruno,Abstract,Invited,HOML},
%    note = {\textbf{[Invited]} },
%    pages = {1--2}
% }

% @article{AustrianComputerSociety,
%    author = {Woltzenlogel Paleo, Bruno},
%    title  = {Automated Verification and Reconstruction of G?del's Proof of God's Existence},
%    journal = {Journal of the Austrian Computer Society},
%    year = {2013},
%    keywords = {Bruno,Invited,S,HOML},
%    pages    = {4--6}
% }
